{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-20 documents/fluorescence.tex
basic run done
nah.

@@

@@

>>>>

Performance of this arrangement was satisfactory. A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts.

@@

Silicon photomultipliers like ON's C−Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.

half-life is 0.693 times the average lifetime.

@@

Another neat technique is to add
